\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{naturalnames}{hyperref}
\documentclass[9pt]{ShumailaAhmed-Resume}
\usepackage{ragged2e}
\usepackage{tikz}
\usepackage{fontenc}
\usepackage{titlesec}
\usepackage[dvipsnames]{xcolor}

\setmainfont[Path = fonts/calibri/]{Calibri}
\titleformat{\subsection}
       {\normalfont\fontsize{10}{17}\bfseries\itshape}{}{1em}{}
\def\checkmark{\tikz\fill[scale=0.3](0,.35) -- (.25,0) -- (1,.7) -- (.25,.15) -- cycle;} 
\begin{document}

\begin{minipage}[t]{0.33\textwidth} 
\begin{large}
	\headername{Shumaila Ahmed}\\
\end{large}
\vspace{2pt}MS Artificial Intelligence NEDUET (P)\\
\vspace{2pt}BE Electronics NEDUET (2017)\\% University Of Engineering $\&$ Technology \\ 
\vspace{2pt}CGPA: 3.312\\
\vspace{2pt}Contact: 03122147357, 03122884451

\vspace{2pt}\ExternalLink Email: \href{mailto:shumailaahmed2014@gmail.com}{{\custombold{shumailaahmed2014@gmail.com}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{\large Links } 
%\noindent\rule{5cm}{0.4pt}\\
\vspace{2pt}{\small \ExternalLink Web:} \href{http://www.pyagonist.com}{\custombold{pyagonist.com}} \\
\vspace{2pt}{\small \ExternalLink Github:} \href{https://github.com/ShumailaAhmed}{\custombold{shumailaahmed}} \\
\vspace{2pt}{\small \ExternalLink LinkedIn:}  \href{https://www.linkedin.com/in/shummi}{\custombold{shumailaahmed}} \\
\vspace{2pt}{\small \ExternalLink StackOverflow:} \href{https://stackoverflow.com/users/14975963/shumaila-ahmed}{\custombold{Shumaila Ahmed}}


\section{\large  SKILLS}

\noindent\rule{5cm}{0.4pt}
%\subsection{OS}
%\vspace{6pt}
\subsection*{ \custombold{Networking}}
{\footnotesize Switches, Routers, Firewall, Network+}
\vspace{2pt}
\subsection*{ \custombold{Cyber Security}}
{\footnotesize Wireshark, OSSIM, Q-radar, ELK, ArcSight, Kali, \\
Suricata, Security+, Linux utilities}
\vspace{2pt}
\subsection*{ \custombold{Languages}}
{\footnotesize C/C\#, Python, JS, R, C++}
\vspace{2pt}
\subsection*{\custombold{Framework}}
{\footnotesize .NET, MVC, ASP, Entity-FW, ADO.NET, ROS}
\vspace{2pt}
\subsection*{\custombold{Front-End/Databases}}
{\footnotesize HTML, CSS, JS, MySQL, SSMS}

\vspace{2pt}
\subsection*{\custombold{AI $\&$ Computer vision}}
{\footnotesize OpenCv, TensorFlow, Tesseract,}\\
{\footnotesize Keras, Theano, Pytorch, Ski-kit Image}\\
{\footnotesize Mxnet, Pandas, sci-kit Learn, CAFFE}
 
\vspace{2pt}
\subsection*{\custombold{Embedded}}
{\footnotesize Raspberry-Pi, Arduino,} \\
{\footnotesize variety of sensor suit}
\vspace{2pt}
\subsection*{\custombold{Premiere General}}
{\footnotesize Leadership, Microsoft Office Suit,}\\
{\footnotesize Teamwork, Latex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{\large  ONLINE CERTIFICATIONS}
\noindent\rule{5cm}{0.4pt}\\
\vspace{2pt}{\checkmark
\small Intro to Cyber Security Specialization}\\
\vspace{2pt}{\checkmark
\small DE, BDM, and ML on GCP Specialization}\\
\vspace{2pt}{\checkmark
\small Self Driving Car Specialization} \\
\vspace{2pt}{\checkmark
\small Deep Learning AI Specialization}\\
\vspace{2pt}{\checkmark
\small Python For Everybody Specialization}\\
\vspace{2pt}{\checkmark
\small Mathematics For Machine Learning}\\
\vspace{2pt}{\checkmark
\small Deep Learning For Computer Vision}\\
\vspace{2pt}{\checkmark
\small R-Programming Course}\\
\vspace{2pt}{\checkmark
\small Machine Learning Course}\\

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 
\hspace*{0mm}\hfill \textbf{\href{}{}}

\section{\hspace{290pt} \large  EXPERIENCE}

\noindent\rule{12.5cm}{0.05mm}

\vspace{3pt}

\datecolor{2021-date} \runsubsection{Team Lead}
\descript{National Center Cyber Security - NEDUET}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
{\small Team and Technical Management of End point security and Network Security Domains. Leading Development of Security Solutions}\\
\descriptright{OS Dev, Linux Package Management, Server and Network Management, TI, SIEM \& SOAR}
\end{minipage}

\vspace{5pt}

\datecolor{2021-date} \runsubsection{Research Associate}
\descript{National Center Cyber Security - NEDUET}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
{\small Working on SIEM Software Development and testing. Core responsibility include migration from monolithic to micro-service architecture.}\\
\descriptright{Python, C, LAMP stack, SQL/NO-SQL DB}
\end{minipage}

\vspace{5pt}

\datecolor{2020-2021} \runsubsection{AI Engineer - Research Assistant}
\descript{National Center of AI - NEDUET}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{3pt}}
{\small Worked on Pakistan's First Autonomous Vehicle Project at Smart City Lab, National Center of Artificial Intelligence (NCAI-NEDUET). Worked with benchmark datasets related to AVs. Managed team of 20+ interns.}\\
\descriptright{Python, Computer Vision, Deep Learning, CARLA, Docker \& ROS}
\end{minipage}

\vspace{5pt}

\datecolor{2017-2020} \runsubsection{Associate Software Engineer}
\descript{SkyLin Consultants}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
{\small Full-Stack services including development and support of various SOAP-Web Services, Proprietary IT Solutions, Web Apps \& research for POCs. Participated in database migration. Managed team of 7 developers, working with different clients.\\
(Jr.Software Developer from 2017 - 2018)}\\
\descriptright{Asp.Net, MCV, C\#, JS, JQ, Html, Css, SSMS, Python \& DS Stack}
\end{minipage}
\sectionsep

\vspace{5pt}

\datecolor{2018-2020} \runsubsection{Freelance Software Developer and Auditor}
\descript{ }
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
{\small Provide various services as freelancer including data attenuation, Web \& Software development and data auditing services (for UK based clients based on GDPR).
}
\end{minipage}

\vspace{5pt}

\datecolor{2015-2016} \runsubsection{Director Team Planning}
\descript{IEEE NEDUET - Student Branch}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
{\small Planned and Executed educational events, trainings and competitions on assorted topics like entrepreneurship, 3d printing, PCB Design etc. } 
\end{minipage}

\vspace{5pt}

\datecolor{2015-2016} \runsubsection{Research Intern}
\descript{ Bio-Robotics Lab NEDUET}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
{\small Worked on Assistive Mobility Cane exploiting skin stretch mechanism for sensor guided navigation to aid visually impaired individuals. Hardware Project}
\end{minipage}
\sectionsep
\descriptright{Arduino, Sonar, Proteus}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{7pt}
\section{\hspace{190pt} \large PATENT, PUBLICATION \& AWARD }
\noindent\rule{12.5cm}{0.1pt}
\vspace{5pt}
\datecolor{2021} \runsubsection{}
\descript{Journal Publication}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{1pt}}
{\small Abbas, A. N., Samad, A., Shumaila Ahmed, \& Siddiqui, U. A. (2021).
A novel clutch coupled drive design for rectification of odometry error: a comparative experimental study. International Journal of Mechatronics and Automation, 8(2), 62-71.}
%\href{https://www.inderscienceonline.com/doi/abs/10.1504/IJMA.2021.115239}{.}
%\textcolor{blue}{\ExternalLink}
\end{minipage}

\vspace{5pt}
\datecolor{2018} \runsubsection{}
\descript{Patent Pending}
\noindent
\hspace{5em}
\begin{minipage}{0.85\textwidth\vspace{1pt}}
{\small A. Nathad, A. Samad, Shumaila Ahmed and U. Abdullah, Mechanically
Synchronized 4-Wheel Drive Vehicle via Clutch, Pakistan.
IPO Filed Dec 6th}
\end{minipage}
\datecolor{2017} \runsubsection{}
\descript{Runner Up}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{1pt}}
{\small DICE National Automotive Innovation Competition
Electronic Considerations of Space Rovers with reusable Image Processing
based navigational modules for Visually Impaired}
\end{minipage}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SIDE PROJECT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}

\newpage % Start a new page
\begin{minipage}[t]{0.33\textwidth} 
\section{\large \uppercase{Trainings \& Pursuits }}
\noindent\rule{5cm}{0.4pt}\\
\vspace{2pt}{\small \checkmark Research in Radiogenomics}\\
\vspace{2pt}{\small \checkmark AI-Computer Vision Seminar}\\
\vspace{2pt}{\small \checkmark AI-Finance Industry Seminar}\\
\vspace{2pt}{\small \checkmark AI-Accounting \& E-Commerce Seminar}\\
\vspace{2pt}{\small \checkmark 8th IEEEP Exhibition \& Conference}\\
\vspace{2pt}{\small \checkmark National Conferences on Space Science}\\
\vspace{2pt}{\small \checkmark PRINT-3D Workshop}\\
\vspace{2pt}{\small \checkmark Drone technology Workshop}\\
\vspace{2pt}{\small \checkmark SPEC-16 Robo Maze} \\
\vspace{2pt}{\small \checkmark SENTEC-15 Robo Maze \& PCB }\\
\vspace{2pt}{\small \checkmark Theater play MOSAIC}\\
\vspace{2pt}{\small \checkmark Point Guard on NED girls Basketball Team}

\end{minipage} 
\begin{minipage}[t]{0.66\textwidth}
\section{\hspace{240pt} \large  {RESEARCH \& PROJECTS}}
\noindent\rule{12.5cm}{0.2pt}

\datecolor{2020-2021} \runsubsection{Environmental Perception for Autonomous Vehicles}
\descript{}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{1pt}}
\begin{justify}

{\small Research on AV sensor fusion for real-time perception requirements, 3D Environmental Reconstruction using pure vision and sensor fusion based techniques, LIDAR based SLAM, etc} 
\end{justify}
\end{minipage}

\datecolor{2018-2019} \runsubsection{Fusion of Computer-Vision \& Brain Machine Interface}
\descript{}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{1pt}}
{\small \justify{ Comprehensive research on IoT device management using concoction of computer vision, emotive
Epoc EEG headset to devise interactive devices to overcome disabilities
for patients of visual impairment, tetraplegia, downs syndrome and autism. }} 
\end{minipage}
\datecolor{2017-2018} \runsubsection{Strategic Robot Localization Exploiting Sensor Fusion}
\descript{}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{1pt}}
{\small A robot localization module using anchor tag system, encoders and digital compass
sensor fusion. Hardware Project}
\end{minipage}
\datecolor{2016-2017} \runsubsection{Smart Rover For Obstacle Avoidance \& Path Planning}
\descript{}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{1pt}}
{\small Exploiting computer vision and neural networks for modeling electronic considerations
of space rovers.
Indoor Environment. Hardware Project}
\end{minipage}
\end{minipage} 
\end{document}  \documentclass[]{article}


